Safe and Robust Formal Synthesis of Digital Controllers for Continuous Plants

### 2018-03-14 automatica/paper.tex
update benchmark description

The \textit{continuous stirred tank reactor} plant describes a linear model for PH dynamics of a PH 
neutralization process of an aqueous solution of sodium acetate with 
hydrochloric acid in a continuous flow stirred-tank reactor. 
The \textit{flexible beam} is a plant employed in vibration studies; the physical system consists of a flexible 
metallic structure with piezoceramic actuators and sensors.
The \textit{helicopter longitudinal motion} plant describes the dynamics of 
transitional motion with respect to a longitudinal plane and the 
rotational motion around the longitudinal axis.
The \textit{USCG cutter tampa heading angle} plant describes the heading angle 
dynamics of a Coast Guard cutter. 
The \textit{voltage regulator} plant consists of a linear model of a synchronous 
machine connected to an  infinite bus~\cite{KOKOTOVIC198023}.

>>>>

There are two \textit{continuous stirred tank reactor} models that describes the PH dynamics of a neutralization 
reaction of an aqueous solution of sodium acetate with  hydrochloric acid (CSTR1)~\cite{cstr} and the temperature of a 
exothermic reaction~\cite{astrom2006advanced} in a continuous flow stirred-tank  reactor. The \textit{bioreactor} 
benchmark is a linear model identified by least squares for the cell mass concentration controlled through dilution 
rate of a bioreactor~\cite{bioreactor}. The \textit{steam drum} benchmark describes the linear model for the 
level dynamics of a  boiler steam drum~\cite{boiler}.
The \textit{flexible beam} is a plant employed in vibration studies; the physical system consists of a flexible 
metallic structure with piezoceramic actuators and sensors.
The \textit{helicopter longitudinal motion} plant describes the dynamics of 
transitional motion with respect to a longitudinal plane and the 
rotational motion around the longitudinal axis.
The \textit{USCG cutter tampa heading angle} plant describes the heading angle 
dynamics of a Coast Guard cutter. 
The \textit{voltage regulator} plant consists of a linear model of a synchronous 
machine connected to an  infinite bus~\cite{KOKOTOVIC198023}.
